An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
another minor phrasing tweak

CloudCoder executes Java, Python, and Ruby code relatively securely using
a Java Security Manager.
(CloudCoder uses Jython\cite{jython} and JRuby\cite{jruby}
to execute Python and Ruby submissions, allowing us to take advantage of
the Java Security Manager for those languages.)
CloudCoder's execution of C/C++ code is somewhat less secure, although 
we hope to take advantage of a better sandboxing mechanism
in the near future, possibly based on the work of
David Malan\cite{Malan:2013:CSS:2445196.2445242} for Harvard's
online CS50 course.  However, because thus far the only users of
CloudCoder have been instructors and students in introductory courses,
the weak sandboxing has not been a significant concern.

>>>>

CloudCoder executes Java, Python, and Ruby code relatively securely using
a Java Security Manager.
(CloudCoder uses Jython\cite{jython} and JRuby\cite{jruby}
to execute Python and Ruby submissions, allowing us to take advantage of
the Java Security Manager for those languages.)
CloudCoder's execution of C/C++ code is somewhat less secure, although 
we hope to take advantage of a better sandboxing mechanism
in the near future, possibly based on the work of
David Malan\cite{Malan:2013:CSS:2445196.2445242} for Harvard's
online CS50 course.  However, because thus far the only users of
CloudCoder have been instructors and students,
the weak sandboxing has not been a significant concern.
